### 2022-08-25 main/chapter_searches.tex
add some notes and references for frequentist section
add note on intuition, correct early mention of Bayes decision rules

In decision theory, we want a mathematical procedure that identifies the
optimal decision to make in a given context.
Although this theory has a long history, we point specifically to the result
by Wald~\cite{
wald1947bayes,
wald1950bayes,
jaynes2003probability
}
that the optimal solution to any decision problem can be framed as the
minimization of an expected cost function, or risk:
\begin{equation}
\label{eqn:searches_bayes_decision_rule}
R(t) = \int\! c(t, x) \,\mathrm{d}p(x)
,
\end{equation}
where we mean `expected' in the mathematical mean sense of a `mean' average.
This cost function $c(t, x)$ evaluates the badness of outcomes for a given
decision $t$ and states of the world $x$ to which context must assign prior
probabilities $p(x)$.
For a given cost function and prior, one should choose the decision $t$ that
minimizes $R(t)$.

Although alternative ideas (such as minimax, minimizing a maximum
loss~\cite{savage1951review}) can empirically work well, the mathematical
statement of this theorem states that restricting oneself to Bayes decision
rules cannot deny access to optimal decisions.
Alternatives can at best be equivalent.

@@

Figure~\ref{fig:searches_significant}

>>>>

In decision theory, we want a mathematical procedure that identifies the
optimal decision to make in a given context.
Although this theory has a long history, we point specifically to the result
by Wald~\cite{
wald1947bayes,
wald1950bayes,
jaynes2003probability
}
that the optimal solution to any decision problem can be framed as the
minimization of an expected cost function, or risk:
\begin{equation}
\label{eqn:searches_bayes_decision_rule}
R(t) = \int\! c(t, x) \,\mathrm{d}p(x)
,
\end{equation}
where we mean `expected' in the mathematical mean sense of a `mean' average.
This cost function $c(t, x)$ evaluates the badness of outcomes for a given
decision $t$ and states of the world $x$ to which context must assign prior
probabilities $p(x)$.
For a given cost function and prior, one should choose the decision $t$ that
minimizes $R(t)$.
More important than this Wald's mathematical proof is that this coincides with
intuition --- when considering decisions, it feels normal to imagine what might
occur in each case and consider how good or bad the plausble outcomes are.

Although alternative ideas (such as minimax, minimizing a maximum
loss~\cite{savage1951review}) can work well in certain contexts, this theorem
states that restricting oneself to minimizing an expected cost function cannot
deny one access to optimal decisions.
Alternative formulations can at best be equivalent.

@@

\TODO{p-value}
Figure~\ref{fig:searches_significant}
\TODO{confidence interval}
\TODO{maximum likelihood}
\TODO{unbiased}

\TODO{likelihood principle ~\cite{
birnbaum1962foundations,
savage1962foundations
}
}
